{\large Gravitational wave sources in our Galactic backyard:}\\{\normalsize Predictions for BHBH, BHNS and NSNS binaries in LISA

### 2021-10-16 paper/tex/sections/appendix.tex
change most of the conclusions with selma :)
clean up all of the figures

\begin{figure}[htb]
    \centering
    \includegraphics[width=\columnwidth]{../figures/fig11_random_simple_galaxy.png}
    \caption{As Fig.~\ref{fig:galaxy_schematic} (right panel), but for the Milky Way model used in \citet{Breivik+2020}.  \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig11_random_simple_galaxy.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/galaxy_creation_station.ipynb}{\faBook}.}
    \label{fig:simple_mw}
\end{figure}

@@

\begin{figure}[htb]
    \centering
    \includegraphics[width=\columnwidth]{../figures/fig12_mBH_simple_mw_variation.pdf}
    \caption{As Fig.~\ref{fig:fiducial_pdf_distributions} (top left panel), but for the Milky Way model used in \citet{Breivik+2020}. Dotted lines show the distribution from Fig.~\ref{fig:fiducial_pdf_distributions} for comparison. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig12_mBH_simple_mw_variation.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
    \label{fig:bh_mass_simple_mw}
\end{figure}

@@

        A & Fiducial & \confinv{124.3}{11.3}{10.7} & \confinv{74.0}{9.0}{9.0} & \confinv{42.4}{6.4}{6.6} & \confinv{7.9}{2.9}{3.1} & \confinv{202.2}{14.2}{13.8} & \confinv{117.9}{10.9}{11.1} & \confinv{71.3}{8.3}{8.7} & \confinv{13.0}{4.0}{4.0}\\

@@

        E & Case BB unstable & \confinv{76.7}{8.7}{8.3} & \confinv{69.3}{8.3}{8.7} & \confinv{7.3}{2.3}{2.7} & \confinv{0.2}{0.2}{0.8} & \confinv{121.4}{11.4}{10.6} & \confinv{109.3}{10.3}{10.7} & \confinv{11.8}{3.8}{3.2} & \confinv{0.4}{0.4}{0.6}\\
        F & E+K & \confinv{320.9}{17.9}{18.1} & \confinv{154.3}{12.3}{12.7} & \confinv{148.4}{12.4}{12.6} & \confinv{18.2}{4.2}{3.8} & \confinv{483.7}{21.7}{22.3} & \confinv{239.5}{15.5}{15.5} & \confinv{216.8}{14.8}{15.2} & \confinv{27.4}{5.4}{5.6}\\
        G & $\alpha_{\rm CE}=0.1$ & \confinv{40.2}{6.2}{6.8} & \confinv{27.9}{4.9}{5.1} & \confinv{2.1}{1.1}{1.9} & \confinv{10.2}{3.2}{2.8} & \confinv{64.1}{8.1}{7.9} & \confinv{43.9}{6.9}{7.1} & \confinv{3.5}{1.5}{1.5} & \confinv{16.7}{3.7}{4.3}\\

@@

        J & $\alpha_{\rm CE}=10.0$ & \confinv{77.9}{8.9}{9.1} & \confinv{26.7}{4.7}{5.3} & \confinv{16.3}{4.3}{3.7} & \confinv{34.9}{5.9}{6.1} & \confinv{126.2}{11.2}{10.8} & \confinv{42.4}{6.4}{6.6} & \confinv{26.6}{5.6}{5.4} & \confinv{57.2}{7.2}{7.8}\\
        K & Optimistic

@@

        L & Fryer Rapid SN & \confinv{127.3}{11.3}{11.7} & \confinv{50.4}{7.4}{6.6} & \confinv{70.2}{8.2}{8.8} & \confinv{6.7}{2.7}{2.3} & \confinv{204.9}{13.9}{14.1} & \confinv{76.6}{8.6}{8.4} & \confinv{117.4}{10.4}{10.6} & \confinv{10.8}{2.8}{3.2}\\
        M & Max $m_{\rm NS}$

@@

        N & Max $m_{\rm NS}$

@@

        O & No PISN & \confinv{126.7}{11.7}{11.3} & \confinv{75.3}{8.3}{8.7} & \confinv{43.4}{6.4}{6.6} & \confinv{8.0}{3.0}{3.0} & \confinv{205.7}{14.7}{14.3} & \confinv{120.5}{10.5}{10.5} & \confinv{72.3}{8.3}{8.7} & \confinv{12.8}{3.8}{3.2}\\

@@

        $30 \, {\rm km s^{-1}}$ & \confinv{268.3}{16.3}{16.7} & \confinv{91.8}{9.8}{9.2} & \confinv{142.9}{11.9}{12.1} & \confinv{33.6}{5.6}{5.4} & \confinv{426.8}{20.8}{21.2} & \confinv{142.9}{11.9}{12.1} & \confinv{229.0}{15.0}{15.0} & \confinv{54.9}{7.9}{7.1}\\
        R & No BH

@@

        T & $f_{\rm WR} = 5$ & \confinv{29.7}{5.7}{5.3} & \confinv{5.7}{2.7}{2.3} & \confinv{15.5}{3.5}{3.5} & \confinv{8.5}{2.5}{2.5} & \confinv{48.8}{6.8}{7.2} & \confinv{9.2}{3.2}{2.8} & \confinv{26.2}{5.2}{4.8} & \confinv{13.4}{3.4}{3.6}\\

@@

    \end{tabular}
    \label{tab:detection_rates}
\end{table*}

% \subsection{Distribution of eccentric sources on sensitivity curve}
\begin{figure*}[b]
    \centering
    \includegraphics[width=\textwidth]{fig13_dcos_on_sc_eccentric_colours.png}
    \caption{As the bottom panels of Fig.~\ref{fig:dcos_on_sc}, but without the density distributions and scatter points are coloured by their eccentricity. We show eccentric sources are located in an offshoot below the $30 \unit{kpc}$ around $2 \unit{mHz}$. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig13_dcos_on_sc_eccentric_colours.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/sensitivity_curve.ipynb}{\faBook}.}
    \label{fig:dcos_on_sc_ecc_col}
\end{figure*}

@@

\begin{figure}[p]
    \centering
    \includegraphics[height=0.85\textheight]{fig15_formation_channels.pdf}
    \caption{Fraction of each DCO type that is formed through different formation channels for all physics variations. Channels are described in detail in \citet{Broekgaarden+2021}. The classic, single core CEE and double core CEE channels all require at least one common-envelope event whilst only `only stable' consists of only stable mass transfer and `other' contains the remaining binaries which are mainly formed from `lucky' supernova kicks that shrink the binary. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig15_formation_channels.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/formation_channels.ipynb}{\faBook}.}
    \label{fig:formation_channels}
\end{figure}

% \subsection{Properties of detectable systems (progenitors and at DCO formation)}
\begin{figure*}[ht]
    \centering
    \includegraphics[width=\textwidth]{progenitor_distributions.pdf}
    \includegraphics[width=0.66\textwidth]{dco_formation_distributions.pdf}
    \caption{As Fig.~\ref{fig:fiducial_pdf_distributions}, but for the properties of the progentiors of detectable systems (top row) and the properties of the detectable systems at DCO formation (bottom row). Note that the $m_{1, {\rm ZAMS}}$ panel uses a log scaled $y$-axis. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/progenitor_distributions.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/dco_formation_distributions.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
    \label{fig:progenitor_and_dco_properties}
\end{figure*}

% \subsection{Detection rates relative to fiducial model}
\begin{figure*}[hb]
    \centering
    \includegraphics[width=\textwidth]{fig14_dco_relative_rates.pdf}
    \caption{Similar to Fig.~\ref{fig:detection_rates}, this shows the \textit{relative} detection rates compared to the fiducial model in order to emphasise how much each DCO is affected by model variations compared to other DCOs. The scatter points show the mean and the shaded areas show the 1-$\sigma$ uncertainty range. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig14_dco_relative_rates.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/detections.ipynb}{\faBook}.}
    \label{fig:dco_relative_rates}
\end{figure*}

>>>>

\begin{figure}[htb]
    \centering
    \includegraphics[width=\columnwidth]{fig14_random_simple_galaxy.png}
    \caption{As Fig.~\ref{fig:galaxy_schematic} (right panel), but for the Milky Way model used in \citet{Breivik+2020}.  \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig14_random_simple_galaxy.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/galaxy_creation_station.ipynb}{\faBook}.}
    \label{fig:simple_mw}
\end{figure}

@@

\begin{figure}[htb]
    \centering
    \includegraphics[width=\columnwidth]{fig15_mBH_simple_mw_variation.pdf}
    \caption{As Fig.~\ref{fig:fiducial_pdf_distributions} (top left panel), but for the Milky Way model used in \citet{Breivik+2020}. Dotted lines show the distribution from Fig.~\ref{fig:fiducial_pdf_distributions} for comparison. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig15_mBH_simple_mw_variation.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
    \label{fig:bh_mass_simple_mw}
\end{figure}

@@

        A & fiducial & \confinv{124.3}{11.3}{10.7} & \confinv{74.0}{9.0}{9.0} & \confinv{42.4}{6.4}{6.6} & \confinv{7.9}{2.9}{3.1} & \confinv{202.2}{14.2}{13.8} & \confinv{117.9}{10.9}{11.1} & \confinv{71.3}{8.3}{8.7} & \confinv{13.0}{4.0}{4.0}\\

@@

E & unstable
case BB & \confinv{76.7}{8.7}{8.3} & \confinv{69.3}{8.3}{8.7} & \confinv{7.3}{2.3}{2.7} & \boldconfinv{0.2}{0.2}{0.8} & \confinv{121.4}{11.4}{10.6} & \confinv{109.3}{10.3}{10.7} & \confinv{11.8}{3.8}{3.2} & \boldconfinv{0.4}{0.4}{0.6}\\
F & E+K & \boldconfinv{320.9}{17.9}{18.1} & \boldconfinv{154.3}{12.3}{12.7} & \boldconfinv{148.4}{12.4}{12.6} & \confinv{18.2}{4.2}{3.8} & \boldconfinv{483.7}{21.7}{22.3} & \boldconfinv{239.5}{15.5}{15.5} & \confinv{216.8}{14.8}{15.2} & \confinv{27.4}{5.4}{5.6}\\
G & $\alpha_{\rm CE}=0.1$ & \confinv{40.2}{6.2}{6.8} & \confinv{27.9}{4.9}{5.1} & \boldconfinv{2.1}{1.1}{1.9} & \confinv{10.2}{3.2}{2.8} & \confinv{64.1}{8.1}{7.9} & \confinv{43.9}{6.9}{7.1} & \boldconfinv{3.5}{1.5}{1.5} & \confinv{16.7}{3.7}{4.3}\\

@@

J & $\alpha_{\rm CE}=10.0$ & \confinv{77.9}{8.9}{9.1} & \confinv{26.7}{4.7}{5.3} & \confinv{16.3}{4.3}{3.7} & \boldconfinv{34.9}{5.9}{6.1} & \confinv{126.2}{11.2}{10.8} & \confinv{42.4}{6.4}{6.6} & \confinv{26.6}{5.6}{5.4} & \boldconfinv{57.2}{7.2}{7.8}\\
K & optimistic

@@

L & rapid SN & \confinv{127.3}{11.3}{11.7} & \confinv{50.4}{7.4}{6.6} & \confinv{70.2}{8.2}{8.8} & \confinv{6.7}{2.7}{2.3} & \confinv{204.9}{13.9}{14.1} & \confinv{76.6}{8.6}{8.4} & \confinv{117.4}{10.4}{10.6} & \confinv{10.8}{2.8}{3.2}\\
M & max $m_{\rm NS}$

@@

N & max $m_{\rm NS}$

@@

O & no PISN & \confinv{126.7}{11.7}{11.3} & \confinv{75.3}{8.3}{8.7} & \confinv{43.4}{6.4}{6.6} & \confinv{8.0}{3.0}{3.0} & \confinv{205.7}{14.7}{14.3} & \confinv{120.5}{10.5}{10.5} & \confinv{72.3}{8.3}{8.7} & \confinv{12.8}{3.8}{3.2}\\

@@

$30 \, {\rm km s^{-1}}$ & \confinv{268.3}{16.3}{16.7} & \confinv{91.8}{9.8}{9.2} & \confinv{142.9}{11.9}{12.1} & \confinv{33.6}{5.6}{5.4} & \confinv{426.8}{20.8}{21.2} & \confinv{142.9}{11.9}{12.1} & \boldconfinv{229.0}{15.0}{15.0} & \confinv{54.9}{7.9}{7.1}\\
R & no BH

@@

T & $f_{\rm WR} = 5$ & \boldconfinv{29.7}{5.7}{5.3} & \boldconfinv{5.7}{2.7}{2.3} & \confinv{15.5}{3.5}{3.5} & \confinv{8.5}{2.5}{2.5} & \boldconfinv{48.8}{6.8}{7.2} & \boldconfinv{9.2}{3.2}{2.8} & \confinv{26.2}{5.2}{4.8} & \confinv{13.4}{3.4}{3.6}\\

@@

    \end{tabular}
    \label{tab:detection_rates}
\end{table*}

@@

\begin{figure}[p]
    \centering
    \includegraphics[height=0.85\textheight]{fig16_formation_channels.pdf}
    \caption{Fraction of each DCO type that is formed through different formation channels for all physics variations. Channels are described in detail in \citet{Broekgaarden+2021}. The classic, single core CEE and double core CEE channels all require at least one common-envelope event whilst only `only stable' consists of only stable mass transfer and `other' contains the remaining binaries which are mainly formed from `lucky' supernova kicks that shrink the binary. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig16_formation_channels.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/formation_channels.ipynb}{\faBook}.}
    \label{fig:formation_channels}
\end{figure}

% \subsection{Distribution of eccentric sources on sensitivity curve}
\begin{figure*}[b]
    \centering
    \includegraphics[width=\textwidth]{fig17_dcos_on_sc_eccentric_colours.png}
    \caption{As the bottom panels of Fig.~\ref{fig:dcos_on_sc}, but without the density distributions and scatter points are coloured by their eccentricity. We show eccentric sources are located in an offshoot below the $30 \unit{kpc}$ around $2 \unit{mHz}$. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig17_dcos_on_sc_eccentric_colours.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/sensitivity_curve.ipynb}{\faBook}.}
    \label{fig:dcos_on_sc_ecc_col}
\end{figure*}

% \subsection{Properties of detectable systems (progenitors and at DCO formation)}
\begin{figure*}[ht]
    \centering
    \includegraphics[width=0.66\textwidth]{fig18_dco_formation_distributions.pdf}
    \caption{As Fig.~\ref{fig:fiducial_pdf_distributions}, but for the properties of the progentiors of detectable systems (top row) and the properties of the detectable systems at DCO formation (bottom row). Note that the $m_{1, {\rm ZAMS}}$ panel uses a log scaled $y$-axis. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig18_dco_formation_distributions.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
    \label{fig:progenitor_and_dco_properties}
\end{figure*}

% \subsection{Detection rates relative to fiducial model}
\begin{figure*}[hb]
    \centering
    \includegraphics[width=\textwidth]{fig19_dco_relative_rates.pdf}
    \caption{Similar to Fig.~\ref{fig:detection_rates}, this shows the \textit{relative} detection rates compared to the fiducial model in order to emphasise how much each DCO is affected by model variations compared to other DCOs. The scatter points show the mean and the shaded areas show the 1-$\sigma$ uncertainty range. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig19_dco_relative_rates.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/detections.ipynb}{\faBook}.}
    \label{fig:dco_relative_rates}
\end{figure*}

### 2021-10-16 paper/tex/sections/comparisons.tex
clean up all of the figures

\begin{figure*}[p]
    \centering
    \includegraphics[width=\textwidth]{fig10_1_compare_dco.png}

@@

    \includegraphics[width=\textwidth]{fig10_2_compare_dco.png}
    \caption{A table comparing previous studies of a similar nature to this work. The works listed in the table are \citet{Nelemans+2001}, \citet{Belczynski+2010}, \citet{Liu+2014}, \citet{Lamberts+2018}, \citet{Sesana+2020}, \citet{Lau+2020}, \citet{Breivik+2020} and \citet{Shao+2021}. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig10_1_compare_dco.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig10_w_compare_dco.png}{\faFileImage}.}
    \label{fig:previous_studies}
\end{figure*}

>>>>

\begin{figure*}[p]
    \centering
    \includegraphics[width=\textwidth]{fig13_1_compare_dco.png}

@@

    \includegraphics[width=\textwidth]{fig13_2_compare_dco.png}
    \caption{A table comparing previous studies of a similar nature to this work. The works listed in the table are \citet{Nelemans+2001}, \citet{Belczynski+2010}, \citet{Liu+2014}, \citet{Lamberts+2018}, \citet{Sesana+2020}, \citet{Lau+2020}, \citet{Breivik+2020} and \citet{Shao+2021}. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig13_1_compare_dco.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig13_w_compare_dco.png}{\faFileImage}.}
    \label{fig:previous_studies}
\end{figure*}

### 2021-10-16 paper/tex/sections/results.tex
adjust other todos
clean up all of the figures

@@

Progenitor distribution figure is Fig.~\ref{fig:progenitor_and_dco_properties}.

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=\columnwidth]{fig5_snr_cumulative_all.pdf}
    \caption{Cumulative number of LISA detections with a given signal-to-noise ratio. Colours indicate LISA mission length and shading shows 1- and 2-$\sigma$ uncertainties (obtained via bootstrapping). \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig5_snr_cumulative_all.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
    \label{fig:snr_dist}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=\columnwidth]{fig5_chirp_mass_uncertainty_all.pdf}
    \caption{As Fig.~\ref{fig:snr_dist}, but for the chirp mass uncertainty. The shaded areas indicate regions with more than 10\% and 100\% uncertainty. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig5_chirp_mass_uncertainty_all.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
    \label{fig:m_c_unc}
\end{figure}

@@

\paragraph{Eccentricities}

\todo{SdM: Proposed additional paragraph.... can we say something compact?  You made a large number of plots and estimates..}

@@

\begin{figure}[htb]
    \centering
    \includegraphics[width=\columnwidth]{fig6_angular_resolution_all.pdf}
    \caption{As Fig.~\ref{fig:snr_dist}, but for the angular resolution. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig6_angular_resolution_all.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
    \label{fig:ang_res}
\end{figure}

>>>>

In Figure~\ref{fig:progenitor_properties}, we show some properties of the progenitors of the LISA detectable DCOs. The top panel shows the inital primary mass and is plotted on a log-scale. We see that the vast majority of NSNSs are formed with progenitor masses below $15 \unit{M_{\rm \odot}}$ and none are formed with masses greater than $30 \unit{M_{\rm \odot}}$. In contrast,

\begin{figure}[htb]
    \centering
    \includegraphics[width=\columnwidth]{fig5_progenitor_distributions.pdf}
    \caption{As Fig.~\ref{fig:fiducial_pdf_distributions}, but for the initial primary mass (top) and inital mass ratio (bottom). \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig5_progenitor_distributions.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
    \label{fig:progenitor_properties}
\end{figure}

@@

\todo{@Selma will review this section}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=\columnwidth]{fig6_snr_cumulative_all.pdf}
    \caption{Cumulative number of LISA detections with a given signal-to-noise ratio. Colours indicate LISA mission length and shading shows 1- and 2-$\sigma$ uncertainties (obtained via bootstrapping). \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig6_snr_cumulative_all.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
    \label{fig:snr_dist}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=\columnwidth]{fig7_chirp_mass_uncertainty_all.pdf}
    \caption{As Fig.~\ref{fig:snr_dist}, but for the chirp mass uncertainty. The shaded areas indicate regions with more than 10\% and 100\% uncertainty. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig7_chirp_mass_uncertainty_all.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
    \label{fig:m_c_unc}
\end{figure}

@@

% \paragraph{Eccentricities}

% \todo{SdM: Proposed additional paragraph.... can we say something compact?  You made a large number of plots and estimates..}

@@

\begin{figure}[htb]
    \centering
    \includegraphics[width=\columnwidth]{fig8_angular_resolution_all.pdf}
    \caption{As Fig.~\ref{fig:snr_dist}, but for the angular resolution. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig8_angular_resolution_all.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
    \label{fig:ang_res}
\end{figure}

### 2021-10-16 paper/tex/sections/variations.tex
clean up all of the figures

\begin{figure*}[p]
    \centering
    \includegraphics[width=\textwidth]{fig7_dco_detections.pdf}
    \caption{The number of expected detections in the LISA mission for different DCO types and model variations. Error bars show the 1- (solid) and 2-$\sigma$ (dotted) Poisson uncertainties. An arrow indicates that the error bar extends to zero. The left axis and grid lines show the number of detections in a 4-year LISA mission and the right axis shows an approximation of the number of detections in a 10-year mission (we scale the axis by $\sqrt{T_{\rm obs}}$, see Table~\ref{tab:detection_rates} for exact rates). Each model is described in further detail in Table~\ref{tab:physics_variations} and details of the fiducial assumptions are in Section~\ref{app:fiducial_physics}. See also Fig.~\ref{fig:dco_relative_rates} and Sec.~\ref{sec:detection_rate_analysis} for a discussion. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig7_dco_detections.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/variations.ipynb}{\faBook}.}
    \label{fig:detection_rates}
\end{figure*}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=\columnwidth]{fig8_lower_mass_gap_rapid_variation.pdf}
    \caption{Comparison of the component mass distribution of LISA detectable DCOs when using the Fryer delayed (model \modFid{}) and rapid (model \modRapid{}) remnant mass prescriptions. Distributions are plotted in the same way as Fig.~\ref{fig:fiducial_pdf_distributions}, except all DCOs types are shown in one curve and each type is weighted by its detection rate in the respective model. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig8_lower_mass_gap_rapid_variation.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/variations.ipynb}{\faBook}.}
    \label{fig:lower_mass_gap_variation}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=\columnwidth]{fig9_ecc_low_kick_variation.pdf}
    \caption{As Fig.~\ref{fig:fiducial_pdf_distributions}d, but for model \modSigLower{}. For comparison, we show the mean distribution for the fiducial model (model \modFid{}) as dashed lines. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig9_ecc_low_kick_variation.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/variations.ipynb}{\faBook}.}
    \label{fig:ecc_low_kick_variation}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=\columnwidth]{wr_wind_mass_variations.pdf}
    \caption{As Fig.~\ref{fig:lower_mass_gap_variation}, but instead varying Wolf-Rayet wind efficiency (models \modWRLow{} and \modWRHigh{}). \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/wr_wind_mass_variations.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/variations.ipynb}{\faBook}.}
    \label{fig:wr_wind_mass_variations}
\end{figure}

>>>>

\begin{figure*}[p]
    \centering
    \includegraphics[width=\textwidth]{fig9_dco_detections.pdf}
    \caption{The number of expected detections in the LISA mission for different DCO types and model variations. Error bars show the 1- (solid) and 2-$\sigma$ (dotted) Poisson uncertainties. An arrow indicates that the error bar extends to zero. The left axis and grid lines show the number of detections in a 4-year LISA mission and the right axis shows an approximation of the number of detections in a 10-year mission (we scale the axis by $\sqrt{T_{\rm obs}}$, see Table~\ref{tab:detection_rates} for exact rates). Each model is described in further detail in Table~\ref{tab:physics_variations} and details of the fiducial assumptions are in Section~\ref{app:fiducial_physics}. See also Fig.~\ref{fig:dco_relative_rates} and Sec.~\ref{sec:detection_rate_analysis} for a discussion. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig9_dco_detections.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/detections.ipynb}{\faBook}.}
    \label{fig:detection_rates}
\end{figure*}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=\columnwidth]{fig10_lower_mass_gap_rapid_variation.pdf}
    \caption{Comparison of the component mass distribution of LISA detectable DCOs when using the Fryer delayed (model \modFid{}) and rapid (model \modRapid{}) remnant mass prescriptions. Distributions are plotted in the same way as Fig.~\ref{fig:fiducial_pdf_distributions}, except all DCOs types are shown in one curve and each type is weighted by its detection rate in the respective model. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig10_lower_mass_gap_rapid_variation.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/variations.ipynb}{\faBook}.}
    \label{fig:lower_mass_gap_variation}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=\columnwidth]{fig11_ecc_low_kick_variation.pdf}
    \caption{As Fig.~\ref{fig:fiducial_pdf_distributions}d, but for model \modSigLower{}. For comparison, we show the mean distribution for the fiducial model (model \modFid{}) as dashed lines. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig11_ecc_low_kick_variation.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/variations.ipynb}{\faBook}.}
    \label{fig:ecc_low_kick_variation}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=\columnwidth]{fig12_wr_wind_mass_variations.pdf}
    \caption{As Fig.~\ref{fig:lower_mass_gap_variation}, but instead varying Wolf-Rayet wind efficiency (models \modWRLow{} and \modWRHigh{}). \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig12_wr_wind_mass_variations.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/variations.ipynb}{\faBook}.}
    \label{fig:wr_wind_mass_variations}
\end{figure}
